---
dataMaid: yes
title: Codebook for data
subtitle: "Susan Wade"
date: 2020-06-30 12:30:46
output: pdf_document
geometry: margin=2cm
documentclass: article
header-includes:
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \renewcommand\familydefault{\sfdefault}
  - \newcommand{\bminione}{\begin{minipage}{0.75 \textwidth}}
  - \newcommand{\bminitwo}{\begin{minipage}{0.25 \textwidth}}
  - \newcommand{\emini}{\end{minipage}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
This dataset is created from the University of California at Irvine Human Activity Recognition dataset. It is the result of calculating the average (mean) of all variables containing the words 'mean' or 'std_dev' (standard deviation) for all subjects and all activities. The UCI HAR dataset is separated into several pieces with subjects, activities separated from the data results and the results divided into testing and training sets.  

This dataset combines subjects, activities, testing and training sets into one dataset, subtracts out the variables (with their results) into a new dataset, and then calculates the mean for each subject, activity, and variable combination. For example, the average value is calculated individually for all subject 1, activity 1 observations, then subject 1, acivity 2 observations, and so on. 

Less cryptic variable names were assigned to the averaged results and all values are output in a table format. 


The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations        180

Number of variables            81
---------------------------------




# Codebook summary table

-----------------------------------------------------------------------------------------------------------------------------
Variable                                                                                         Class    # unique   Missing    
                                                                                                           values                        
---------------------------------------------------------------------------------------------- ---------- --------- ---------
**[subject]**                                                                                    integer      30      0.00 %

**[activity]**                                                                                   factor       6       0.00 %

**[mean\_time\_body\_acceleration\_X]**                                                          numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_Y]**                                                          numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_Z]**                                                          numeric      180     0.00 %

**[std\_dev\_time\_body\_acceleration\_X]**                                                      numeric      180     0.00 %

**[std\_dev\_time\_body\_acceleration\_Y]**                                                      numeric      180     0.00 %

**[std\_dev\_time\_body\_acceleration\_Z]**                                                      numeric      180     0.00 %

**[mean\_time\_gravity\_acceleration\_X]**                                                       numeric      180     0.00 %

**[mean\_time\_gravity\_acceleration\_Y]**                                                       numeric      180     0.00 %

**[mean\_time\_gravity\_acceleration\_Z]**                                                       numeric      180     0.00 %

**[std\_dev\_time\_gravity\_acceleration\_X]**                                                   numeric      180     0.00 %

**[std\_dev\_time\_gravity\_acceleration\_Y]**                                                   numeric      180     0.00 %

**[std\_dev\_time\_gravity\_acceleration\_Z]**                                                   numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_jerk\_X]**                                                    numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_jerk\_Y]**                                                    numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_jerk\_Z]**                                                    numeric      180     0.00 %

**[std\_dev\_body\_acceleration\_jerk\_X]**                                                      numeric      180     0.00 %

**[std\_dev\_body\_acceleration\_jerk\_Y]**                                                      numeric      180     0.00 %

**[std\_dev\_body\_acceleration\_jerk\_Z]**                                                      numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_X]**                                                     numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_Y]**                                                     numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_Z]**                                                     numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_X]**                                                 numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_Y]**                                                 numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_Z]**                                                 numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_jerk\_X]**                                               numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_jerk\_Y]**                                               numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_jerk\_Z]**                                               numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_jerk\_X]**                                           numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_jerk\_Y]**                                           numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_jerk\_Z]**                                           numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_magnitude]**                                                  numeric      180     0.00 %

**[std\_dev\_time\_body\_acceleration\_magnitude]**                                              numeric      180     0.00 %

**[mean\_time\_gravity\_acceleration\_magnitude]**                                               numeric      180     0.00 %

**[std\_dev\_time\_gravity\_acceleration\_magnitude]**                                           numeric      180     0.00 %

**[mean\_time\_body\_acceleration\_jerk\_magnitude]**                                            numeric      180     0.00 %

**[std\_dev\_time\_body\_acceleration\_jerk\_magnitude]**                                        numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_magnitude]**                                             numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_magnitude]**                                         numeric      180     0.00 %

**[mean\_time\_body\_angular\_velocity\_jerk\_magnitude]**                                       numeric      180     0.00 %

**[std\_dev\_time\_body\_angular\_velocity\_jerk\_magnitude]**                                   numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_X]**                                                     numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_Y]**                                                     numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_Z]**                                                     numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_X]**                                                 numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_Y]**                                                 numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_Z]**                                                 numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_X]**                                           numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_Y]**                                           numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_Z]**                                           numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_jerk\_X]**                                               numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_jerk\_Y]**                                               numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_jerk\_Z]**                                               numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_jerk\_X]**                                           numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_jerk\_Y]**                                           numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_jerk\_Z]**                                           numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_X]**                                     numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_Y]**                                     numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_Z]**                                     numeric      180     0.00 %

**[mean\_frequency\_body\_angular\_velocity\_X]**                                                numeric      180     0.00 %

**[mean\_frequency\_body\_angular\_velocity\_Y]**                                                numeric      180     0.00 %

**[mean\_frequency\_body\_angular\_velocity\_Z]**                                                numeric      180     0.00 %

**[std\_dev\_frequency\_body\_angular\_velocity\_X]**                                            numeric      180     0.00 %

**[std\_dev\_frequency\_body\_angular\_velocity\_Y]**                                            numeric      180     0.00 %

**[std\_dev\_frequency\_body\_angular\_velocity\_Z]**                                            numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_angular\_velocity\_X]**                                      numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_angular\_velocity\_Y]**                                      numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_angular\_velocity\_Z]**                                      numeric      180     0.00 %

**[mean\_frequency\_body\_acceleration\_magnitude]**                                             numeric      180     0.00 %

**[std\_dev\_frequency\_body\_acceleration\_magnitude]**                                         numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_acceleration\_magnitude]**                                   numeric      180     0.00 %

**[mean\_frequency\_body\_body\_acceleration\_jerk\_magnitude]**                                 numeric      180     0.00 %

**[std\_dev\_frequency\_body\_body\_acceleration\_jerk\_magnitude]**                             numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_body\_acceleration\_jerk\_magnitude]**                       numeric      180     0.00 %

**[mean\_frequency\_body\_body\_angular\_velocity\_magnitude]**                                  numeric      180     0.00 %

**[std\_dev\_frequency\_body\_body\_angular\_velocity\_magnitude]**                              numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_body\_angular\_velocity\_magnitude]**                        numeric      180     0.00 %

**[mean\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude]**                            numeric      180     0.00 %

**[std\_dev\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude]**                        numeric      180     0.00 %

**[mean\_of\_mean\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude]**                  numeric      180     0.00 %
---------------------------------------------------------------------------------------------------------------------------------




# Variable list
## subject  
A numerical identifier for each subject that participated in the study. Thirty individuals between the ages of 19 and 48 took part in the study and are numbered 1-30. 

\bminione 

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               integer

Number of missing obs.      0 (0 %)

Number of unique values          30

Units                           N/A

Median                         15.5

1st and 3rd quartiles         8; 23

Min. and max.                 1; 30
-----------------------------------


\emini
\bminitwo
```{r 'Var-1-subject', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25
), xmax = c(5, 10, 15, 20, 25, 30), ymin = c(0, 0, 0, 0, 0, 0
), ymax = c(30L, 30L, 30L, 30L, 30L, 30L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "subject")
```

\emini




\fullline

## activity  
A character identifier for each activity. The six activities are listed below as 'observed factors'

\bminione  

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                 factor

Number of missing obs.       0 (0 %)

Number of unique values            6

Units                           N/A

Mode                        "laying"

Reference category            laying
------------------------------------


\emini
\bminitwo
```{r 'Var-2-activity', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("laying", 
"sitting", "standing", "walking", "walking_downstairs", "walking_upstairs"
), class = "factor"), y = c(30L, 30L, 30L, 30L, 30L, 30L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "activity")
```

\emini


- Observed factor levels: \"laying\", \"sitting\", \"standing\", \"walking\", \"walking_downstairs\", \"walking_upstairs\". 



\fullline

## mean\_time\_body\_acceleration\_X
A numeric value representing average body acceleration in the x-direction in the time domain.

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Units                      gravity (g)

Median                            0.28

1st and 3rd quartiles       0.27; 0.28

Min. and max.                0.22; 0.3
--------------------------------------


\emini
\bminitwo
```{r 'Var-3-mean-time-body-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0.22, 0.23, 0.24, 0.25, 
0.26, 0.27, 0.28, 0.29, 0.3), xmax = c(0.23, 0.24, 0.25, 0.26, 
0.27, 0.28, 0.29, 0.3, 0.31), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(1L, 2L, 7L, 11L, 21L, 93L, 30L, 14L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_time_body_acceleration_X")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_Y
A numeric value representing average body acceleration in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.02

1st and 3rd quartiles       -0.02; -0.01

Min. and max.                   -0.04; 0
----------------------------------------


\emini
\bminitwo
```{r 'Var-4-mean-time-body-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.045, -0.04, -0.035, 
-0.03, -0.025, -0.02, -0.015, -0.01, -0.005), xmax = c(-0.04, 
-0.035, -0.03, -0.025, -0.02, -0.015, -0.01, -0.005, 0), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 0L, 6L, 15L, 25L, 87L, 
30L, 14L, 2L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "mean_time_body_acceleration_Y")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_Z
A numeric value representing average body acceleration in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.11

1st and 3rd quartiles        -0.11; -0.1

Min. and max.               -0.15; -0.08
----------------------------------------


\emini
\bminitwo
```{r 'Var-5-mean-time-body-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.16, -0.15, -0.14, 
-0.13, -0.12, -0.11, -0.1, -0.09, -0.08), xmax = c(-0.15, -0.14, 
-0.13, -0.12, -0.11, -0.1, -0.09, -0.08, -0.07), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 1L, 2L, 15L, 48L, 92L, 
16L, 3L, 1L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "mean_time_body_acceleration_Z")
```

\emini




\fullline

## std\_dev\_time\_body\_acceleration\_X
A numeric value representing the standard deviation of body acceleration in the x-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.63
---------------------------------------


\emini
\bminitwo
```{r 'Var-6-std-dev-time-body-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 8L, 37L, 20L, 16L, 7L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_time_body_acceleration_X")
```

\emini




\fullline

## std\_dev\_time\_body\_acceleration\_Y
A numeric value representing the standard deviation of body acceleration in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.03

Min. and max.                -0.99; 0.62
----------------------------------------


\emini
\bminitwo
```{r 'Var-7-std-dev-time-body-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 0L, 10L, 43L, 24L, 10L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_time_body_acceleration_Y")
```

\emini




\fullline

## std\_dev\_time\_body\_acceleration\_Z
A numeric value representing the standard deviation of body acceleration in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.23

Min. and max.                -0.99; 0.61
----------------------------------------


\emini
\bminitwo
```{r 'Var-8-std-dev-time-body-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 15L, 42L, 20L, 10L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_time_body_acceleration_Z")
```

\emini




\fullline

## mean\_time\_gravity\_acceleration\_X
A numeric value representing the average gravity acceleration in the x-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.92

1st and 3rd quartiles        0.84; 0.94

Min. and max.               -0.68; 0.97
---------------------------------------


\emini
\bminitwo
```{r 'Var-9-mean-time-gravity-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.8, -0.6, -0.4, -0.2, 
0, 0.2, 0.4, 0.6, 0.8), xmax = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 
0.6, 0.8, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 
13L, 9L, 6L, 0L, 0L, 1L, 6L, 143L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_time_gravity_acceleration_X")
```

\emini




\fullline

## mean\_time\_gravity\_acceleration\_Y
A numeric value representing the average gravity acceleration in the y-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.13

1st and 3rd quartiles       -0.23; 0.09

Min. and max.               -0.48; 0.96
---------------------------------------


\emini
\bminitwo
```{r 'Var-10-mean-time-gravity-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), xmax = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 66L, 61L, 
14L, 11L, 5L, 10L, 10L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_time_gravity_acceleration_Y")
```

\emini




\fullline

## mean\_time\_gravity\_acceleration\_Z
A numeric value representing the average gravity acceleration in the z-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.02

1st and 3rd quartiles       -0.12; 0.15

Min. and max.                -0.5; 0.96
---------------------------------------


\emini
\bminitwo
```{r 'Var-11-mean-time-gravity-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), xmax = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 18L, 60L, 
63L, 13L, 7L, 10L, 6L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_time_gravity_acceleration_Z")
```

\emini




\fullline

## std\_dev\_time\_gravity\_acceleration\_X
A numeric value representing the standard deviation of gravity acceleration in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.97

1st and 3rd quartiles       -0.98; -0.95

Min. and max.                  -1; -0.83
----------------------------------------


\emini
\bminitwo
```{r 'Var-12-std-dev-time-gravity-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.98, -0.96, -0.94, 
-0.92, -0.9, -0.88, -0.86, -0.84), xmax = c(-0.98, -0.96, -0.94, 
-0.92, -0.9, -0.88, -0.86, -0.84, -0.82), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(55L, 52L, 52L, 12L, 4L, 3L, 1L, 0L, 
1L)), class = "data.frame", row.names = c(NA, -9L)), vnam = "std_dev_time_gravity_acceleration_X")
```

\emini




\fullline

## std\_dev\_time\_gravity\_acceleration\_Y
A numeric value representing the standard deviation of gravity acceleration in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.96

1st and 3rd quartiles       -0.97; -0.94

Min. and max.               -0.99; -0.64
----------------------------------------


\emini
\bminitwo
```{r 'Var-13-std-dev-time-gravity-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.95, -0.9, -0.85, 
-0.8, -0.75, -0.7, -0.65), xmax = c(-0.95, -0.9, -0.85, -0.8, 
-0.75, -0.7, -0.65, -0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(107L, 72L, 0L, 0L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_gravity_acceleration_Y")
```

\emini




\fullline

## std\_dev\_time\_gravity\_acceleration\_Z
A numeric value representing the standard deviation of gravity acceleration in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.95

1st and 3rd quartiles       -0.96; -0.92

Min. and max.               -0.99; -0.61
----------------------------------------


\emini
\bminitwo
```{r 'Var-14-std-dev-time-gravity-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.95, -0.9, -0.85, 
-0.8, -0.75, -0.7, -0.65), xmax = c(-0.95, -0.9, -0.85, -0.8, 
-0.75, -0.7, -0.65, -0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(79L, 76L, 23L, 1L, 0L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_gravity_acceleration_Z")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_jerk\_X
A numeric value that represents the average jerk, a value derived from body acceleration in the x-direction in the time domain.

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Units                      gravity (g)

Median                            0.08

1st and 3rd quartiles       0.07; 0.08

Min. and max.               0.04; 0.13
--------------------------------------


\emini
\bminitwo
```{r 'Var-15-mean-time-body-acceleration-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0.04, 0.05, 0.06, 0.07, 
0.08, 0.09, 0.1, 0.11, 0.12, 0.13), xmax = c(0.05, 0.06, 0.07, 
0.08, 0.09, 0.1, 0.11, 0.12, 0.13, 0.14), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(3L, 4L, 13L, 98L, 34L, 14L, 8L, 5L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -10L)), vnam = "mean_time_body_acceleration_jerk_X")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_jerk\_Y
A numeric value that represents the average jerk, a value derived from body acceleration in the y-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.01

1st and 3rd quartiles           0; 0.01

Min. and max.               -0.04; 0.06
---------------------------------------


\emini
\bminitwo
```{r 'Var-16-mean-time-body-acceleration-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.04, -0.03, -0.02, 
-0.01, 0, 0.01, 0.02, 0.03, 0.04, 0.05), xmax = c(-0.03, -0.02, 
-0.01, 0, 0.01, 0.02, 0.03, 0.04, 0.05, 0.06), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 3L, 13L, 26L, 52L, 59L, 
18L, 6L, 0L, 1L)), class = "data.frame", row.names = c(NA, -10L
)), vnam = "mean_time_body_acceleration_jerk_Y")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_jerk\_Z
A numeric value that represents the average jerk, a value derived from body acceleration in the z-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                                0

1st and 3rd quartiles          -0.01; 0

Min. and max.               -0.07; 0.04
---------------------------------------


\emini
\bminitwo
```{r 'Var-17-mean-time-body-acceleration-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.07, -0.06, -0.05, 
-0.04, -0.03, -0.02, -0.01, 0, 0.01, 0.02, 0.03), xmax = c(-0.06, 
-0.05, -0.04, -0.03, -0.02, -0.01, 0, 0.01, 0.02, 0.03, 0.04), 
    ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 1L, 
    1L, 6L, 12L, 27L, 77L, 41L, 9L, 3L, 2L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "mean_time_body_acceleration_jerk_Z")
```

\emini




\fullline

## std\_dev\_body\_acceleration\_jerk\_X
A numeric value that represents the standard deviation of jerk, a value derived from body acceleration in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.54
----------------------------------------


\emini
\bminitwo
```{r 'Var-18-std-dev-body-acceleration-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
15L, 31L, 26L, 13L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_body_acceleration_jerk_X")
```

\emini




\fullline

## std\_dev\_body\_acceleration\_jerk\_Y
A numeric value that represents the standard deviation of jerk, a value derived from body acceleration in the y-direction in the time domain

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.78

1st and 3rd quartiles       -0.97; -0.15

Min. and max.                -0.99; 0.36
----------------------------------------


\emini
\bminitwo
```{r 'Var-19-std-dev-body-acceleration-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 10L, 28L, 
    32L, 12L, 7L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_body_acceleration_jerk_Y")
```

\emini




\fullline

## std\_dev\_body\_acceleration\_jerk\_Z
A numeric value that represents the standard deviation of jerk, a value derived from body acceleration in the z-direction in the time domain

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.51

Min. and max.                -0.99; 0.03
----------------------------------------


\emini
\bminitwo
```{r 'Var-20-std-dev-body-acceleration-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), xmax = c(-0.9, -0.8, 
-0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 11L, 16L, 19L, 
18L, 16L, 2L, 3L, 3L, 1L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "std_dev_body_acceleration_jerk_Z")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_X
A numeric value representing the average body's angular velocity in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.03

1st and 3rd quartiles       -0.05; -0.02

Min. and max.                -0.21; 0.19
----------------------------------------


\emini
\bminitwo
```{r 'Var-21-mean-time-body-angular-velocity-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.25, -0.2, -0.15, 
-0.1, -0.05, 0, 0.05, 0.1, 0.15), xmax = c(-0.2, -0.15, -0.1, 
-0.05, 0, 0.05, 0.1, 0.15, 0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 18L, 20L, 113L, 11L, 13L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_time_body_angular_velocity_X")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_Y
A numeric value representing the average body angular velocity in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.07

1st and 3rd quartiles       -0.09; -0.06

Min. and max.                 -0.2; 0.03
----------------------------------------


\emini
\bminitwo
```{r 'Var-22-mean-time-body-angular-velocity-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.22, -0.2, -0.18, 
-0.16, -0.14, -0.12, -0.1, -0.08, -0.06, -0.04, -0.02, 0, 0.02
), xmax = c(-0.2, -0.18, -0.16, -0.14, -0.12, -0.1, -0.08, -0.06, 
-0.04, -0.02, 0, 0.02, 0.04), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 1L, 2L, 5L, 5L, 12L, 38L, 72L, 23L, 
9L, 5L, 5L, 2L)), class = "data.frame", row.names = c(NA, -13L
)), vnam = "mean_time_body_angular_velocity_Y")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_Z
A numeric value representing the average body angular velocity in the z-direction in the time domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       radians/sec

Median                             0.09

1st and 3rd quartiles         0.07; 0.1

Min. and max.               -0.07; 0.18
---------------------------------------


\emini
\bminitwo
```{r 'Var-23-mean-time-body-angular-velocity-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.08, -0.06, -0.04, 
-0.02, 0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16), xmax = c(-0.06, 
-0.04, -0.02, 0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16, 
0.18), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
1L, 1L, 3L, 2L, 4L, 11L, 36L, 74L, 23L, 8L, 13L, 3L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "mean_time_body_angular_velocity_Z")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_X
A numeric value representing the standard deviation of the body angular velocity in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.44

Min. and max.                -0.99; 0.27
----------------------------------------


\emini
\bminitwo
```{r 'Var-24-std-dev-time-body-angular-velocity-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 4L, 51L, 31L, 
    3L, 0L, 1L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_time_body_angular_velocity_X")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_Y
A numeric value representing the standard deviation of the body angular velocity in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.48
----------------------------------------


\emini
\bminitwo
```{r 'Var-25-std-dev-time-body-angular-velocity-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 6L, 
43L, 18L, 12L, 8L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_body_angular_velocity_Y")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_Z
A numeric value representing the standard deviation of the body angular velocity in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.31

Min. and max.                -0.99; 0.56
----------------------------------------


\emini
\bminitwo
```{r 'Var-26-std-dev-time-body-angular-velocity-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
20L, 42L, 20L, 3L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_body_angular_velocity_Z")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_jerk\_X
A numeric value that represents the average jerk, a value derived from body angular velocity in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                              -0.1

1st and 3rd quartiles        -0.1; -0.09

Min. and max.               -0.16; -0.02
----------------------------------------


\emini
\bminitwo
```{r 'Var-27-mean-time-body-angular-velocity-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.16, -0.14, -0.12, 
-0.1, -0.08, -0.06, -0.04), xmax = c(-0.14, -0.12, -0.1, -0.08, 
-0.06, -0.04, -0.02), ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(10L, 
10L, 55L, 76L, 16L, 7L, 6L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "mean_time_body_angular_velocity_jerk_X")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_jerk\_Y
A numeric value that represents the average jerk, a value derived from body angular velocity in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.04

1st and 3rd quartiles       -0.05; -0.04

Min. and max.               -0.08; -0.01
----------------------------------------


\emini
\bminitwo
```{r 'Var-28-mean-time-body-angular-velocity-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.08, -0.07, -0.06, 
-0.05, -0.04, -0.03, -0.02), xmax = c(-0.07, -0.06, -0.05, -0.04, 
-0.03, -0.02, -0.01), ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(5L, 
5L, 21L, 78L, 62L, 6L, 3L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "mean_time_body_angular_velocity_jerk_Y")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_jerk\_Z
A numeric value that represents the average jerk, a value derived from body angular velocity in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.05

1st and 3rd quartiles       -0.06; -0.05

Min. and max.               -0.09; -0.01
----------------------------------------


\emini
\bminitwo
```{r 'Var-29-mean-time-body-angular-velocity-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.1, -0.09, -0.08, 
-0.07, -0.06, -0.05, -0.04, -0.03, -0.02, -0.01), xmax = c(-0.09, 
-0.08, -0.07, -0.06, -0.05, -0.04, -0.03, -0.02, -0.01, 0), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 1L, 17L, 33L, 74L, 36L, 
11L, 4L, 1L, 1L)), class = "data.frame", row.names = c(NA, -10L
)), vnam = "mean_time_body_angular_velocity_jerk_Z")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_jerk\_X
A numeric value that represents the standard deviation of jerk, a value derived from body angular velocity in the x-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.46

Min. and max.                   -1; 0.18
----------------------------------------


\emini
\bminitwo
```{r 'Var-30-std-dev-time-body-angular-velocity-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 3L, 13L, 20L, 18L, 14L, 15L, 4L, 0L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "std_dev_time_body_angular_velocity_jerk_X")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_jerk\_Y
A numeric value that represents the standard deviation of jerk, a value derived from body angular velocity in the y-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.59

Min. and max.                    -1; 0.3
----------------------------------------


\emini
\bminitwo
```{r 'Var-31-std-dev-time-body-angular-velocity-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(97L, 36L, 30L, 10L, 
    5L, 1L, 1L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_time_body_angular_velocity_jerk_Y")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_jerk\_Z
A numeric value that represents the standard deviation of jerk, a value derived from body angular velocity in the z-direction in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.86

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                   -1; 0.19
----------------------------------------


\emini
\bminitwo
```{r 'Var-32-std-dev-time-body-angular-velocity-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 4L, 14L, 18L, 20L, 17L, 8L, 4L, 1L, 2L, 2L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "std_dev_time_body_angular_velocity_jerk_Z")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_magnitude
A numeric value that represents the average magnitude of body acceleration.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------


\emini
\bminitwo
```{r 'Var-33-mean-time-body-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
0L, 2L, 17L, 37L, 26L, 8L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_time_body_acceleration_magnitude")
```

\emini




\fullline

## std\_dev\_time\_body\_acceleration\_magnitude
A numeric value that represents the standard deviation of the magnitude of body acceleration.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------


\emini
\bminitwo
```{r 'Var-34-std-dev-time-body-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 2L, 
12L, 34L, 21L, 13L, 8L, 2L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_body_acceleration_magnitude")
```

\emini




\fullline

## mean\_time\_gravity\_acceleration\_magnitude
A numeric value that represents the average magnitude of gravity acceleration in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------


\emini
\bminitwo
```{r 'Var-35-mean-time-gravity-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
0L, 2L, 17L, 37L, 26L, 8L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_time_gravity_acceleration_magnitude")
```

\emini




\fullline

## std\_dev\_time\_gravity\_acceleration\_magnitude
A numeric value that represents the standard deviation of magnitude of gravity acceleration in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------


\emini
\bminitwo
```{r 'Var-36-std-dev-time-gravity-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 2L, 
12L, 34L, 21L, 13L, 8L, 2L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_gravity_acceleration_magnitude")
```

\emini




\fullline

## mean\_time\_body\_acceleration\_jerk\_magnitude
A numeric value that represents the average jerk, a value derived from the magnitude of body acceleration in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.82

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                -0.99; 0.43
----------------------------------------


\emini
\bminitwo
```{r 'Var-37-mean-time-body-acceleration-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
17L, 33L, 29L, 7L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_time_body_acceleration_jerk_magnitude")
```

\emini




\fullline

## std\_dev\_time\_body\_acceleration\_jerk\_magnitude
A numeric value that represents the standard deviation of jerk, a value derived from the magnitude of body acceleration in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                              -0.8

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.45
----------------------------------------


\emini
\bminitwo
```{r 'Var-38-std-dev-time-body-acceleration-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
20L, 26L, 26L, 12L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_time_body_acceleration_jerk_magnitude")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_magnitude
A numeric value that represents the average magnitude of body angular velocity in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.66

1st and 3rd quartiles       -0.95; -0.22

Min. and max.                -0.98; 0.42
----------------------------------------


\emini
\bminitwo
```{r 'Var-39-mean-time-body-angular-velocity-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 0L, 
7L, 42L, 28L, 11L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_time_body_angular_velocity_magnitude")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_magnitude
A numeric value that represents the standard deviation of the magnitude of body angular velocity in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.74

1st and 3rd quartiles       -0.95; -0.36

Min. and max.                 -0.98; 0.3
----------------------------------------


\emini
\bminitwo
```{r 'Var-40-std-dev-time-body-angular-velocity-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 32L, 38L, 
    14L, 2L, 2L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_time_body_angular_velocity_magnitude")
```

\emini




\fullline

## mean\_time\_body\_angular\_velocity\_jerk\_magnitude
A numeric value that represents the average jerk, a value derived from the magnitude of body acceleration in the time domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.86

1st and 3rd quartiles       -0.99; -0.51

Min. and max.                   -1; 0.09
----------------------------------------


\emini
\bminitwo
```{r 'Var-41-mean-time-body-angular-velocity-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), xmax = c(-0.9, -0.8, 
-0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 0L, 6L, 19L, 26L, 
16L, 12L, 4L, 3L, 2L, 2L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "mean_time_body_angular_velocity_jerk_magnitude")
```

\emini




\fullline

## std\_dev\_time\_body\_angular\_velocity\_jerk\_magnitude
A numeric value that represents the standard deviation of jerk, a value derived from the magnitude of body angular velocity in the time domain.$

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.25
----------------------------------------


\emini
\bminitwo
```{r 'Var-42-std-dev-time-body-angular-velocity-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
3L, 15L, 20L, 21L, 14L, 5L, 5L, 3L, 2L, 1L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "std_dev_time_body_angular_velocity_jerk_magnitude")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_X
A numeric value representing average body acceleration in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.77

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                   -1; 0.54
----------------------------------------


\emini
\bminitwo
```{r 'Var-43-mean-frequency-body-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
9L, 36L, 23L, 16L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_acceleration_X")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_Y
A numeric value representing average body acceleration in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.59

1st and 3rd quartiles       -0.95; -0.06

Min. and max.                -0.99; 0.52
----------------------------------------


\emini
\bminitwo
```{r 'Var-44-mean-frequency-body-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
1L, 14L, 40L, 25L, 7L, 3L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_acceleration_Y")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_Z
A numeric value representing average body acceleration in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.72

1st and 3rd quartiles       -0.96; -0.32

Min. and max.                -0.99; 0.28
----------------------------------------


\emini
\bminitwo
```{r 'Var-45-mean-frequency-body-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 28L, 40L, 
    13L, 5L, 2L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "mean_frequency_body_acceleration_Z")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_X
A numeric value representing standard deviation body acceleration in the x-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                        gravity (g)

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.66
---------------------------------------


\emini
\bminitwo
```{r 'Var-46-std-dev-frequency-body-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 7L, 37L, 22L, 13L, 7L, 3L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_frequency_body_acceleration_X")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_Y
A numeric value representing standard deviation body acceleration in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.08

Min. and max.                -0.99; 0.56
----------------------------------------


\emini
\bminitwo
```{r 'Var-47-std-dev-frequency-body-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
0L, 14L, 41L, 24L, 8L, 3L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_frequency_body_acceleration_Y")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_Z
A numeric value representing standard deviation body acceleration in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.64

1st and 3rd quartiles       -0.95; -0.27

Min. and max.                -0.99; 0.69
----------------------------------------


\emini
\bminitwo
```{r 'Var-48-std-dev-frequency-body-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 19L, 40L, 19L, 9L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_frequency_body_acceleration_Z")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_X
A numeric value representing average body acceleration in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.26

1st and 3rd quartiles       -0.39; -0.06

Min. and max.                -0.64; 0.16
----------------------------------------


\emini
\bminitwo
```{r 'Var-49-mean-of-mean-frequency-body-acceleration-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1), xmax = c(-0.6, -0.5, -0.4, -0.3, -0.2, 
-0.1, 0, 0.1, 0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
12L, 31L, 37L, 25L, 19L, 27L, 23L, 5L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_of_mean_frequency_body_acceleration_X")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_Y
A numeric value representing average body acceleration in the y-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.01

1st and 3rd quartiles       -0.08; 0.09

Min. and max.               -0.38; 0.47
---------------------------------------


\emini
\bminitwo
```{r 'Var-50-mean-of-mean-frequency-body-acceleration-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.4, -0.3, -0.2, -0.1, 
0, 0.1, 0.2, 0.3, 0.4), xmax = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3, 0.4, 0.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 
8L, 28L, 41L, 59L, 22L, 14L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_of_mean_frequency_body_acceleration_Y")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_Z
A numeric value representing average body acceleration in the z-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.07

1st and 3rd quartiles       -0.04; 0.18

Min. and max.                -0.52; 0.4
---------------------------------------


\emini
\bminitwo
```{r 'Var-51-mean-of-mean-frequency-body-acceleration-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4), xmax = c(-0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 3L, 2L, 12L, 13L, 26L, 50L, 
34L, 28L, 8L, 1L)), class = "data.frame", row.names = c(NA, -11L
)), vnam = "mean_of_mean_frequency_body_acceleration_Z")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_jerk\_X
A numeric value that represents the average of jerk, a value derived from the body acceleration in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.28

Min. and max.                -0.99; 0.47
----------------------------------------


\emini
\bminitwo
```{r 'Var-52-mean-frequency-body-acceleration-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
21L, 35L, 23L, 6L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_acceleration_jerk_X")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_jerk\_Y
A numeric value that represents the average of jerk, a value derived from the body acceleration in the y-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.78

1st and 3rd quartiles       -0.97; -0.2

Min. and max.               -0.99; 0.28
---------------------------------------


\emini
\bminitwo
```{r 'Var-53-mean-frequency-body-acceleration-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 14L, 28L, 
    34L, 9L, 3L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "mean_frequency_body_acceleration_jerk_Y")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_jerk\_Z
A numeric value that represents the average of jerk, a value derived from the body acceleration in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.87

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                -0.99; 0.16
----------------------------------------


\emini
\bminitwo
```{r 'Var-54-mean-frequency-body-acceleration-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 6L, 17L, 15L, 17L, 16L, 11L, 3L, 2L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "mean_frequency_body_acceleration_jerk_Z")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_jerk\_X
A numeric value that represents the standard deviation of jerk, a value derived from the body acceleration in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                   -1; 0.48
----------------------------------------


\emini
\bminitwo
```{r 'Var-55-std-dev-frequency-body-acceleration-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
21L, 30L, 25L, 11L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_frequency_body_acceleration_jerk_X")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_jerk\_Y
A numeric value that represents the standard deviation of jerk, a value derived from the body acceleration in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.17

Min. and max.                -0.99; 0.35
----------------------------------------


\emini
\bminitwo
```{r 'Var-56-std-dev-frequency-body-acceleration-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 11L, 28L, 
    33L, 9L, 7L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_frequency_body_acceleration_jerk_Y")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_jerk\_Z
A numeric value that represents the standard deviation of jerk, a value derived from the body acceleration in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                              -0.9

1st and 3rd quartiles       -0.98; -0.54

Min. and max.               -0.99; -0.01
----------------------------------------


\emini
\bminitwo
```{r 'Var-57-std-dev-frequency-body-acceleration-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1), xmax = c(-0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 13L, 20L, 22L, 15L, 10L, 
3L, 1L, 4L)), class = "data.frame", row.names = c(NA, -10L)), 
    vnam = "std_dev_frequency_body_acceleration_jerk_Z")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_X
A numeric value that represents the average of average jerk, a value derived from the body acceleration in the x-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.06

1st and 3rd quartiles       -0.29; 0.18

Min. and max.               -0.58; 0.33
---------------------------------------


\emini
\bminitwo
```{r 'Var-58-mean-of-mean-frequency-body-acceleration-jerk-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3), xmax = c(-0.5, -0.4, -0.3, -0.2, 
-0.1, 0, 0.1, 0.2, 0.3, 0.4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(3L, 12L, 29L, 34L, 10L, 5L, 20L, 33L, 29L, 5L
)), class = "data.frame", row.names = c(NA, -10L)), vnam = "mean_of_mean_frequency_body_acceleration_jerk_X")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_Y
A numeric value that represents the average of average jerk, a value derived from the body acceleration in the y-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.23

1st and 3rd quartiles       -0.4; -0.05

Min. and max.                 -0.6; 0.2
---------------------------------------


\emini
\bminitwo
```{r 'Var-59-mean-of-mean-frequency-body-acceleration-jerk-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1), xmax = c(-0.6, -0.5, -0.4, -0.3, -0.2, 
-0.1, 0, 0.1, 0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
13L, 31L, 28L, 25L, 20L, 34L, 24L, 4L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_of_mean_frequency_body_acceleration_jerk_Y")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_jerk\_Z
A numeric value that represents the average of average jerk, a value derived from the body acceleration in the z-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                            -0.09

1st and 3rd quartiles       -0.31; 0.04

Min. and max.               -0.63; 0.23
---------------------------------------


\emini
\bminitwo
```{r 'Var-60-mean-of-mean-frequency-body-acceleration-jerk-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.6, -0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0, 0), ymax = c(3L, 8L, 14L, 25L, 15L, 21L, 28L, 51L, 14L, 
1L)), class = "data.frame", row.names = c(NA, -10L)), vnam = "mean_of_mean_frequency_body_acceleration_jerk_Z")
```

\emini




\fullline

## mean\_frequency\_body\_angular\_velocity\_X
A numeric value that represents the average body angular velocity in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.73

1st and 3rd quartiles       -0.97; -0.34

Min. and max.                -0.99; 0.47
----------------------------------------


\emini
\bminitwo
```{r 'Var-61-mean-frequency-body-angular-velocity-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
29L, 41L, 16L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_angular_velocity_X")
```

\emini




\fullline

## mean\_frequency\_body\_angular\_velocity\_Y
A numeric value that represents the average body angular velocity in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.81

1st and 3rd quartiles       -0.97; -0.45

Min. and max.                -0.99; 0.33
----------------------------------------


\emini
\bminitwo
```{r 'Var-62-mean-frequency-body-angular-velocity-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 13L, 38L, 22L, 
    10L, 6L, 1L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "mean_frequency_body_angular_velocity_Y")
```

\emini




\fullline

## mean\_frequency\_body\_angular\_velocity\_Z
A numeric value that represents the average body angular velocity in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.79

1st and 3rd quartiles       -0.96; -0.26

Min. and max.                -0.99; 0.49
----------------------------------------


\emini
\bminitwo
```{r 'Var-63-mean-frequency-body-angular-velocity-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
17L, 41L, 21L, 6L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_angular_velocity_Z")
```

\emini




\fullline

## std\_dev\_frequency\_body\_angular\_velocity\_X
A numeric value that represents the stadard deviation of body angular velocity in the x-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.48

Min. and max.                 -0.99; 0.2
----------------------------------------


\emini
\bminitwo
```{r 'Var-64-std-dev-frequency-body-angular-velocity-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(85L, 
5L, 1L, 10L, 28L, 21L, 22L, 6L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "std_dev_frequency_body_angular_velocity_X")
```

\emini




\fullline

## std\_dev\_frequency\_body\_angular\_velocity\_Y
A numeric value that represents the stadard deviation of body angular velocity in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.65
----------------------------------------


\emini
\bminitwo
```{r 'Var-65-std-dev-frequency-body-angular-velocity-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
4L, 42L, 21L, 12L, 8L, 2L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "std_dev_frequency_body_angular_velocity_Y")
```

\emini




\fullline

## std\_dev\_frequency\_body\_angular\_velocity\_Z
A numeric value that represents the stadard deviation of body angular velocity in the z-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.82

1st and 3rd quartiles       -0.96; -0.39

Min. and max.                -0.99; 0.52
----------------------------------------


\emini
\bminitwo
```{r 'Var-66-std-dev-frequency-body-angular-velocity-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 5L, 
37L, 36L, 6L, 4L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "std_dev_frequency_body_angular_velocity_Z")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_angular\_velocity\_X
A numeric value that represents the average of the average of body angular velocity in the x-direction of the frequency domain.

\bminione

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Units                      radians/sec

Median                           -0.12

1st and 3rd quartiles         -0.21; 0

Min. and max.               -0.4; 0.25
--------------------------------------


\emini
\bminitwo
```{r 'Var-67-mean-of-mean-frequency-body-angular-velocity-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.4, -0.3, -0.2, -0.1, 
0, 0.1, 0.2), xmax = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3), ymin = c(0, 
0, 0, 0, 0, 0, 0), ymax = c(14L, 37L, 50L, 33L, 22L, 20L, 4L)), class = "data.frame", row.names = c(NA, 
-7L)), vnam = "mean_of_mean_frequency_body_angular_velocity_X")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_angular\_velocity\_Y
A numeric value that represents the average of the average of body angular velocity in the y-direction of the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.16

1st and 3rd quartiles       -0.29; -0.04

Min. and max.                -0.67; 0.27
----------------------------------------


\emini
\bminitwo
```{r 'Var-68-mean-of-mean-frequency-body-angular-velocity-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.6, -0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0, 0), ymax = c(3L, 4L, 9L, 27L, 24L, 51L, 29L, 23L, 7L, 3L
)), class = "data.frame", row.names = c(NA, -10L)), vnam = "mean_of_mean_frequency_body_angular_velocity_Y")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_angular\_velocity\_Z
A numeric value that represents the average of the average of body angular velocity in the z-direction of the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       radians/sec

Median                            -0.05

1st and 3rd quartiles       -0.15; 0.04

Min. and max.               -0.51; 0.38
---------------------------------------


\emini
\bminitwo
```{r 'Var-69-mean-of-mean-frequency-body-angular-velocity-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.5, -0.4, -0.3, 
-0.2, -0.1, 0, 0.1, 0.2, 0.3), xmax = c(-0.5, -0.4, -0.3, -0.2, 
-0.1, 0, 0.1, 0.2, 0.3, 0.4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(2L, 4L, 7L, 19L, 38L, 42L, 38L, 18L, 9L, 3L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "mean_of_mean_frequency_body_angular_velocity_Z")
```

\emini




\fullline

## mean\_frequency\_body\_acceleration\_magnitude
A numeric value that represents the average magnitude of body acceleration in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.67

1st and 3rd quartiles       -0.96; -0.16

Min. and max.                -0.99; 0.59
----------------------------------------


\emini
\bminitwo
```{r 'Var-70-mean-frequency-body-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
10L, 31L, 22L, 16L, 9L, 2L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_acceleration_magnitude")
```

\emini




\fullline

## std\_dev\_frequency\_body\_acceleration\_magnitude
A numeric value that represents the stadard deviation of the magnitude of body acceleration in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.37

Min. and max.                -0.99; 0.18
----------------------------------------


\emini
\bminitwo
```{r 'Var-71-std-dev-frequency-body-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(82L, 
6L, 1L, 3L, 13L, 20L, 20L, 8L, 8L, 9L, 7L, 3L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "std_dev_frequency_body_acceleration_magnitude")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_acceleration\_magnitude
A numeric value that represents the average of the average magnitude of body acceleration in the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                        gravity (g)

Median                             0.08

1st and 3rd quartiles       -0.01; 0.17

Min. and max.               -0.31; 0.44
---------------------------------------


\emini
\bminitwo
```{r 'Var-72-mean-of-mean-frequency-body-acceleration-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.4, -0.3, -0.2, -0.1, 
0, 0.1, 0.2, 0.3, 0.4), xmax = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3, 0.4, 0.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
3L, 16L, 33L, 52L, 40L, 26L, 8L, 1L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "mean_of_mean_frequency_body_acceleration_magnitude")
```

\emini




\fullline

## mean\_frequency\_body\_body\_acceleration\_jerk\_magnitude
A numeric value that represents the average jerk, a value derived from the magnitude of body acceleration in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.79

1st and 3rd quartiles       -0.98; -0.19

Min. and max.                -0.99; 0.54
----------------------------------------


\emini
\bminitwo
```{r 'Var-73-mean-frequency-body-body-acceleration-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
16L, 25L, 26L, 17L, 4L, 1L)), class = "data.frame", row.names = c(NA, 
-8L)), vnam = "mean_frequency_body_body_acceleration_jerk_magnitude")
```

\emini




\fullline

## std\_dev\_frequency\_body\_body\_acceleration\_jerk\_magnitude
A numeric value that represents the standard deviation of jerk, a value derived from the magnitude of body acceleration in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        gravity (g)

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.27

Min. and max.                -0.99; 0.32
----------------------------------------


\emini
\bminitwo
```{r 'Var-74-std-dev-frequency-body-body-acceleration-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 25L, 22L, 
    27L, 12L, 3L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_frequency_body_body_acceleration_jerk_magnitude")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_body\_acceleration\_jerk\_magnitude
A numeric value that represents the average of the average jerk, a value derived from the magnitude of body acceleration in the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       gravity (g)

Median                             0.17

1st and 3rd quartiles        0.05; 0.28

Min. and max.               -0.13; 0.49
---------------------------------------


\emini
\bminitwo
```{r 'Var-75-mean-of-mean-frequency-body-body-acceleration-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.15, -0.1, -0.05, 
0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45), xmax = c(-0.1, 
-0.05, 0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45, 0.5
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 
6L, 18L, 21L, 16L, 19L, 24L, 18L, 20L, 18L, 12L, 3L, 2L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "mean_of_mean_frequency_body_body_acceleration_jerk_magnitude")
```

\emini




\fullline

## mean\_frequency\_body\_body\_angular\_velocity\_magnitude
A numeric value that represents the average body angular velocity magnitude in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.77

1st and 3rd quartiles       -0.96; -0.41

Min. and max.                 -0.99; 0.2
----------------------------------------


\emini
\bminitwo
```{r 'Var-76-mean-frequency-body-body-angular-velocity-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 
2L, 0L, 8L, 20L, 18L, 22L, 9L, 4L, 5L, 1L, 2L, 1L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "mean_frequency_body_body_angular_velocity_magnitude")
```

\emini




\fullline

## std\_dev\_frequency\_body\_body\_angular\_velocity\_magnitude
A numeric value that represents the standard deviation of body angular velocity magnitude in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.77

1st and 3rd quartiles       -0.95; -0.43

Min. and max.                -0.98; 0.24
----------------------------------------


\emini
\bminitwo
```{r 'Var-77-std-dev-frequency-body-body-angular-velocity-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(80L, 
10L, 1L, 6L, 18L, 24L, 23L, 7L, 7L, 2L, 1L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "std_dev_frequency_body_body_angular_velocity_magnitude")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_body\_angular\_velocity\_magnitude
A numeric value that represents the average of average of body angular velocity magnitude in the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       radians/sec

Median                            -0.05

1st and 3rd quartiles       -0.17; 0.08

Min. and max.               -0.46; 0.41
---------------------------------------


\emini
\bminitwo
```{r 'Var-78-mean-of-mean-frequency-body-body-angular-velocity-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.5, -0.4, -0.3, -0.2, 
-0.1, 0, 0.1, 0.2, 0.3, 0.4), xmax = c(-0.4, -0.3, -0.2, -0.1, 
0, 0.1, 0.2, 0.3, 0.4, 0.5), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(2L, 9L, 17L, 48L, 34L, 27L, 21L, 13L, 7L, 2L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "mean_of_mean_frequency_body_body_angular_velocity_magnitude")
```

\emini




\fullline

## mean\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude
A numeric value that represents the average of the average jerk, a value derived from the magnitude of body angular velocity in the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.15
----------------------------------------


\emini
\bminitwo
```{r 'Var-79-mean-frequency-body-body-angular-velocity-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
2L, 15L, 22L, 18L, 15L, 6L, 5L, 4L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-12L)), vnam = "mean_frequency_body_body_angular_velocity_jerk_magnitude")
```

\emini




\fullline

## std\_dev\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude
A numeric value that represents the standard deviation of jerk, a value derived from the magnitude of body angular velocityin the frequency domain.

\bminione

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Units                        radians/sec

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.61

Min. and max.                   -1; 0.29
----------------------------------------


\emini
\bminitwo
```{r 'Var-80-std-dev-frequency-body-body-angular-velocity-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(94L, 41L, 29L, 10L, 
    5L, 0L, 1L)), class = "data.frame", row.names = c(NA, -7L
)), vnam = "std_dev_frequency_body_body_angular_velocity_jerk_magnitude")
```

\emini




\fullline

## mean\_of\_mean\_frequency\_body\_body\_angular\_velocity\_jerk\_magnitude
A numeric value that represents the average of the average jerk, a value derived from the magnitude of body angular velocity in the frequency domain.

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Units                       radians/sec

Median                             0.11

1st and 3rd quartiles        0.05; 0.21

Min. and max.               -0.18; 0.43
---------------------------------------


\emini
\bminitwo
```{r 'Var-81-mean-of-mean-frequency-body-body-angular-velocity-jerk-magnitude', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.2, -0.15, -0.1, -0.05, 
0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4), xmax = c(-0.15, 
-0.1, -0.05, 0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
4L, 5L, 8L, 23L, 40L, 25L, 23L, 28L, 12L, 9L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-13L)), vnam = "mean_of_mean_frequency_body_body_angular_velocity_jerk_magnitude")
```

\emini




\fullline





